Demonstration of matching route networks

### 2024-02-01 r/demo.qmd
Add more examples

```{r}
# devtools::load_all()
# remotes::install_dev("rsgeo")
# remotes::install_dev("stplanr")
```

```{r}
library(stplanr)
library(tmap)
library(sf)
library(rsgeo)
rnet_y = route_network_small["flow"]
rnet_y$id = 1:nrow(rnet_y)
# The target object
rnet_x = rnet_subset(osm_net_example[1], rnet_y)
# Get start and end points for each linestring in rnet_x:
rnet_x_s = lwgeom::st_startpoint(rnet_x)
rnet_x_e = lwgeom::st_endpoint(rnet_x)
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["flow"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```
```{}

@@

rnet_xp <- line_segment(rnet_xp, segment_length = 10)
rnet_yp <- line_segment(rnet_yp, segment_length = 10)

@@

tmap_mode("view") # Set to view for interactive mode

brks = c(0, 50, 100, 200, 500,1000,2000)
m1 = tm_shape(rnet_intersection_complex) + tm_lines("commute_fastest_bicycle_go_dutch", palette = "viridis", breaks = brks)
m2 = tm_shape(rnet_merged) + tm_lines("commute_fastest_bicycle_go_dutch", palette = "viridis", breaks = brks)
tmap_arrange(m1, m2, nrow = 1, sync = TRUE)

@@

## With `{geos}`

@@

tmap_mode("view") # Set to view for interactive mode

@@

```{r}
rnet_x = rnet_x_projected
rnet_y = rnet_y_projected
distance = 9
dist_chop = 0.1
rnet_join = function(
    rnet_x,
    rnet_y,
    distance = 9,
    dist_chop = 0.1
    ) {
  # Check CRS is projected:
  stopifnot(
    sf::st_is_longlat(rnet_x) == FALSE,
    sf::st_is_longlat(rnet_y) == FALSE
  )
  rnet_x_geos = geos::as_geos_geometry(rnet_x)
  rnet_y_geos = geos::as_geos_geometry(rnet_y)
  params = geos::geos_buffer_params(end_cap_style = "flat")
  rnet_x_buffer = geos::geos_buffer(rnet_x_geos, distance, params = params)
  rnet_xbl = geos::geos_boundary(rnet_x_buffer)
  rnet_xblb = geos::geos_buffer(rnet_xbl, dist_chop, params = params)
  rnet_xlbc = geos::geos_make_collection(rnet_xblb)
  rnet_xlbcu = geos::geos_unary_union(rnet_xlbc)
  rnet_y_chopped = geos::geos_difference(
    rnet_y_geos,
    rnet_xlbcu
  )
  rnet_ycj = geos::geos_inner_join_keys(
    rnet_y_chopped,
    rnet_x_buffer
  )
  rnet_y_df = sf::st_drop_geometry(rnet_y)
  rnet_y_df_expanded = rnet_y_df[rnet_ycj$x, ]
  rnet_y_df_expanded$id_x = rnet_x_df[[1]][rnet_ycj$y]
  # Replace 'id_x' with the name of the first column in rnet_x_df:
  nx = which(names(rnet_y_df_expanded) == "id_x")
  new_name = names(rnet_x_df)[1]
  names(rnet_y_df_expanded)[nx] = new_name
  rnet_y_df_expanded
}
# Test it:
res = rnet_join(rnet_x, rnet_y)
res
res |>
  dplyr::group_by(id) |>
  dplyr::summarise(
    osm_ids = paste(osm_id, collapse = ", ")
  )

@@

```{r}
rnet_x = sf::read_sf("https://github.com/ropensci/stplanr/releases/download/v1.0.2/rnet_x_ed.geojson")
rnet_y = sf::read_sf("https://github.com/ropensci/stplanr/releases/download/v1.0.2/rnet_y_ed.geojson")
```

```{r}
plot(rnet_y["value"], lwd = 5)
```

```{r}
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["value"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

```{r}
# Stplanr implementation:
system.time({
rnet_merged = rnet_merge(rnet_x, rnet_y["value"], dist = 9, segment_length = 20, funs = list(value = sum))
})
plot(rnet_merged["value"], lwd = 3)
```

```{r}
rnet_xp = rnet_x |>
  sf::st_transform("EPSG:27700")
rnet_yp = rnet_y |>
  sf::st_transform("EPSG:27700") 
system.time({
rnet_matched = rnet_join_geos(rnet_xp, rnet_yp, distance = 9, dist_chop = 1)
rnet_matched_agg = rnet_matched |>
  dplyr::group_by(identifier) |>
  dplyr::summarise(value = sum(value))
rnet_joined = rnet_x |>
  dplyr::left_join(rnet_matched_agg)
})
summary(rnet_joined)
# rnet_joined$value
plot(rnet_joined["value"], lwd = 3)
```

@@

```{r}
# remotes::install_github("josiahparry/rsgeo", ref = "rent")

>>>>

```{r}
devtools::load_all()
# remotes::install_dev("rsgeo")
# remotes::install_dev("stplanr")
```

```{r}
library(stplanr)
library(tmap)
library(sf)
library(rsgeo)
rnet_y = route_network_small["flow"]
rnet_y$id = 1:nrow(rnet_y)
# The target object
rnet_x = rnet_subset(osm_net_example[1], rnet_y)
# Get start and end points for each linestring in rnet_x:
rnet_x_s = lwgeom::st_startpoint(rnet_x)
rnet_x_e = lwgeom::st_endpoint(rnet_x)
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["flow"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

# rnet_xp <- line_segment(rnet_xp, segment_length = 10)
# rnet_yp <- line_segment(rnet_yp, segment_length = 10)

@@

tmap_mode("plot") # Set to view for interactive mode

brks = c(0, 50, 100, 200, 500,1000,2000)
m1 = tm_shape(rnet_intersection_complex) + tm_lines("commute_fastest_bicycle_go_dutch", palette = "viridis", breaks = brks, lwd = 5)
m2 = tm_shape(rnet_merged) + tm_lines("commute_fastest_bicycle_go_dutch", palette = "viridis", breaks = brks, lwd = 5)
tmap_arrange(m1, m2, nrow = 1, sync = TRUE)

@@

## `rnet_join_geos`

```{r}
rnet_xp = rnet_xp |> 
  dplyr::mutate(identifier = 1:nrow(rnet_xp)) |> 
  dplyr::select(identifier, dplyr::everything())
rnet_yp = rnet_yp |> 
  dplyr::transmute(value = commute_fastest_bicycle_go_dutch)
rnet_matched = rnet_join_geos(rnet_xp, rnet_yp, distance = 9, dist_chop = 1)
rnet_matched_agg = rnet_matched |>
  dplyr::group_by(identifier) |>
  dplyr::summarise(value = sum(value))
rnet_joined = rnet_xp |>
  dplyr::left_join(rnet_matched_agg)
summary(rnet_joined)
# rnet_joined$value
plot(rnet_joined["value"], lwd = 3)
plot(rnet_yp["value"], lwd = 3)
plot(rnet_matched)
```

## With `{geos}`: details

@@

tmap_mode("plot") # Set to view for interactive mode

@@

```{r}
#| eval: false
rnet_x = rnet_x_projected
rnet_y = rnet_y_projected
distance = 9
dist_chop = 0.1
rnet_join = function(
    rnet_x,
    rnet_y,
    distance = 9,
    dist_chop = 0.1
    ) {
  # Check CRS is projected:
  stopifnot(
    sf::st_is_longlat(rnet_x) == FALSE,
    sf::st_is_longlat(rnet_y) == FALSE
  )
  rnet_x_geos = geos::as_geos_geometry(rnet_x)
  rnet_y_geos = geos::as_geos_geometry(rnet_y)
  params = geos::geos_buffer_params(end_cap_style = "flat")
  rnet_x_buffer = geos::geos_buffer(rnet_x_geos, distance, params = params)
  rnet_xbl = geos::geos_boundary(rnet_x_buffer)
  rnet_xblb = geos::geos_buffer(rnet_xbl, dist_chop, params = params)
  rnet_xlbc = geos::geos_make_collection(rnet_xblb)
  rnet_xlbcu = geos::geos_unary_union(rnet_xlbc)
  rnet_y_chopped = geos::geos_difference(
    rnet_y_geos,
    rnet_xlbcu
  )
  rnet_ycj = geos::geos_inner_join_keys(
    rnet_y_chopped,
    rnet_x_buffer
  )
  rnet_y_df = sf::st_drop_geometry(rnet_y)
  rnet_y_df_expanded = rnet_y_df[rnet_ycj$x, ]
  rnet_y_df_expanded$id_x = rnet_x_df[[1]][rnet_ycj$y]
  # Replace 'id_x' with the name of the first column in rnet_x_df:
  nx = which(names(rnet_y_df_expanded) == "id_x")
  new_name = names(rnet_x_df)[1]
  names(rnet_y_df_expanded)[nx] = new_name
  rnet_y_df_expanded
}
# Test it:
res = rnet_join(rnet_x, rnet_y)
res
res |>
  dplyr::group_by(id) |>
  dplyr::summarise(
    osm_ids = paste(osm_id, collapse = ", ")
  )

@@

```{r}
#| eval: false
rnet_x = sf::read_sf("https://github.com/ropensci/stplanr/releases/download/v1.0.2/rnet_x_ed.geojson")
rnet_y = sf::read_sf("https://github.com/ropensci/stplanr/releases/download/v1.0.2/rnet_y_ed.geojson")
```

```{r}
#| eval: false
plot(rnet_y["value"], lwd = 5)
```

```{r}
#| eval: false
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["value"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

```{r}
#| eval: false
# Stplanr implementation:
system.time({
rnet_merged = rnet_merge(rnet_x, rnet_y["value"], dist = 9, segment_length = 20, funs = list(value = sum))
})
plot(rnet_merged["value"], lwd = 3)
```

```{r}
#| eval: false
rnet_xp = rnet_x |>
  sf::st_transform("EPSG:27700")
rnet_yp = rnet_y |>
  sf::st_transform("EPSG:27700") 
system.time({
rnet_matched = rnet_join_geos(rnet_xp, rnet_yp, distance = 9, dist_chop = 1)
rnet_matched_agg = rnet_matched |>
  dplyr::group_by(identifier) |>
  dplyr::summarise(value = sum(value))
rnet_joined = rnet_x |>
  dplyr::left_join(rnet_matched_agg)
})
summary(rnet_joined)
# rnet_joined$value
plot(rnet_joined["value"], lwd = 3)
```

@@

```{r}
#| eval: false
# remotes::install_github("josiahparry/rsgeo", ref = "rent")
